---
title: "Lab1 - Hello R"
author: "Hannah Crawley"
date: "01/17/2025"
output: 
  html_document: 
    theme: flatly
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

1846 rows and 3 variables a.k.a. columns 
Varaibles include: dataset i.e., which dataset the data comes from, x-values, and y-values 
#Frequency table 
```{r}
datasaurus_dozen %>% 
  count(dataset) %>% 
  print(13)
#> # A tibble:
#> #   13 × 2
#>    dataset   
#>    <chr>     
#>  1 away      
#>  2 bullseye  
#>  3 circle    
#>  4 dino      
#>  5 dots      
#>  6 h_lines   
#>  7 high_lines
#>  8 slant_down
#>  9 slant_up  
#> 10 star      
#> 11 v_lines   
#> 12 wide_lines
#> 13 x_shape   
#> # ℹ 1 more
#> #   variable:
#> #   n <int>
```


### Exercise 2

Plotting dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating corr (r):

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Note to self: Dinosaurs are not linear r = - 0.06


### Exercise 3

```{r plot-star}
Star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = Star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Note to self: capitalization matters 
```{r cor-star}
Star_data %>%
  summarize(r = cor(x, y))
```
Star and dino have roughly the same correlation r = -0.06

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

More of an ellipse than a circle, but the correlation is the same as the other two data sets r = -0.06

### Exercise 5

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```
 #faceting makes a grid with several charts 

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
 Correlations are all very similar, if not the same  
